Climate Prediction Markets and Convergence of Predictive Models

### 2015-06-15 prediction_market.tex
added temporal evolution results to paper

\documentclass{article}

\begin{document}

@@

\begin{figure}[h]
\centering
<<pc_sa, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE>>=
load("output/pc2.Rda")
correct_bias <- function(x) {
  x_corr <- x[["original"]] - x[["bias"]]
  min_ci <- x[["min. c.i."]]
  max_ci <- x[["max. c.i."]]
  x <- cbind(x_corr = x_corr, min_ci = min_ci, max_ci = max_ci, x)
  cbind(var = row.names(x), x)
}
plot_pc <- function(x, outcome_var = "Outcome", 
                    xlab = "Variable"){
  ss <- correct_bias(x[[7]]) # $SRRC, $SRC, $PRRC, $PRC

  ggplot2::ggplot(ss, ggplot2::aes(x = var, y = x_corr)) + ggplot2::geom_point() +
    ggplot2::xlab(xlab) + ggplot2::ylab("Partial Rank Correlation Coefficient ") +
    ggplot2::ggtitle(paste("Estimated Effects on", outcome_var)) +
    ggplot2::geom_errorbar(ggplot2::aes(ymax = max_ci, ymin = min_ci), width=0.25) +
    ggplot2::geom_hline(yintercept = 0) +
    ggplot2::ylim(c(-1,1)) +
    ggplot2::theme_bw()
}

plot_pc(pc2, outcome_var = "Convergence of Beliefs", xlab="")
@
\caption{Partial rank correlation coefficient analysis based on 10,000 simulated parameter sets \cite{pujol_sensitivity:_2014,saltelli_sensitivity_2009} of the effects of ideology, market completeness, number of edges in social network, number of traders in market, risk taking propensities, segregation measure of the social network, and the true climate model on the convergence of traders' beliefs. Lines are bootstrapped 95\% confidence intervals.}
\label{fig:pc_sa}
\end{figure}

\begin{figure}
\centering
<<hist, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE, fig.width=9, fig.height=6>>=
sample_count <- 7000
load("output/d.Rda")
library(ggplot2)
d$true.model <- factor(d$true.model, levels = c(0,1), 
                       labels = c("Natural Change", "Human-Induced"))
library(plyr)
cdat <- plyr::ddply(d, "true.model", summarize, outcome_summary = median(convergence))
ggplot2::ggplot(d, aes(x = convergence, fill = true.model)) + 
  geom_density(alpha = 0.3) +
  # xlim(c(-0.6, 0.6)) +
  ylab("Density") + xlab("Convergence of Beliefs") + 
  scale_fill_discrete(name="True Model") + 
  ggtitle(paste(formatC(sample_count, big.mark=','), 
                "Convergence of Belief Outcomes with LHS Input Parameters")) +
  geom_vline(data=cdat, aes(xintercept= outcome_summary,  color = true.model),
             linetype="dashed", size=1) + 
  theme_bw() + 
  theme(legend.justification=c(0,1), legend.position=c(0,1)) 
@
\caption{Density of \Sexpr{formatC(sample_count, big.mark=',')} convergence of belief model outcomes with \Sexpr{formatC(sample_count, big.mark=',')} Latin Hypercube Sampled input parameter sets. \Sexpr{formatC(sum(ifelse(d$true.model=="Human-Induced", 1, 0)), big.mark=',')} of the Latin Hypercube Sampled input parameter sets have ``human-induced'' climate change as the true model and \Sexpr{formatC(sum(ifelse(d$true.model=="Natural Change", 1, 0)), big.mark=',')} have ``natural change'' climate change as the true model. Dashed lines are the medians of the two densities (\Sexpr{cdat$outcome_summary[1]}, \Sexpr{cdat$outcome_summary[2]}). Possible values of convergence of beliefs range from -1 to 1.}
\label{fig:hist}
\end{figure}

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{figure}[h]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/pc_sa-1}

\end{knitrout}
\caption{Partial rank correlation coefficient analysis based on 10,000 simulated parameter sets \cite{pujol_sensitivity:_2014,saltelli_sensitivity_2009} of the effects of ideology, market completeness, number of edges in social network, number of traders in market, risk taking propensities, segregation measure of the social network, and the true climate model on the convergence of traders' beliefs. Lines are bootstrapped 95\% confidence intervals.}
\label{fig:pc_sa}
\end{figure}

\begin{figure}
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/hist-1}

\end{knitrout}
\caption{Density of 7,000 convergence of belief model outcomes with 7,000 Latin Hypercube Sampled input parameter sets. 3,500 of the Latin Hypercube Sampled input parameter sets have ``human-induced'' climate change as the true model and 3,500 have ``natural change'' climate change as the true model. Dashed lines are the medians of the two densities (0, 0.11). Possible values of convergence of beliefs range from -1 to 1.}
\label{fig:hist}
\end{figure}

\begin{figure}
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/temporal-1}

\end{knitrout}
\caption{Temporal evolution of convergence of beliefs.}
\label{fig:temporal}
\end{figure}
